QRF Covariate Selection

### 2020-06-18 analysis/R_scripts/fit_qrf_model.Rmd
updated spawner recruit parameters in QRFcapacity repo, so updated the results here.

data("spawn_rec_data")
# fit Beverton-Holt curve with capacity fixed at QRF capacity prediction
qrf_params = spawn_recr_data %>%
  group_by(Population) %>%
  nest() %>%
  left_join(qrf_caps,
            by = c('Population' = 'Trap')) %>%
  filter(!is.na(tot_cap)) %>%
  mutate(form = 'QRF',
         inits = map2(.x = data,
                      .y = tot_cap,
                     .f = function(x, y) {
                       inits = srStarts(Parr ~ Spawners,
                                        data = x,
                                        type = 'BevertonHolt',
                                        param = 3)

@@

spawn_rec_params %<>%
  bind_rows(qrf_params)

>>>>

data("spawn_recr_data")
# fit Beverton-Holt curve with capacity fixed at QRF capacity prediction
qrf_params = spawn_recr_data %>%
  group_by(Population) %>%
  nest() %>%
  left_join(qrf_caps,
            by = c('Population' = 'Trap')) %>%
  filter(!is.na(tot_cap)) %>%
  mutate(form = 'QRF',
         inits = map2(.x = data,
                      .y = tot_cap,
                     .f = function(x, y) {
                       inits = srStarts(Parr ~ Spawners,
                                        data = x,
                                        type = 'BevertonHolt',
                                        param = 3)

@@

spawn_rec_params %<>%
  bind_rows(qrf_params %>%
              select(one_of(names(spawn_rec_params)))) %>%
  arrange(Population, form)
